Standardization of ceramic shape: A case study of Iron Age pottery from northeastern Taiwan

### 2020-09-18 analysis/paper/paper.Rmd
removed some repetitive figures

```{r, size-shape-regression-plots, echo=FALSE, fig.cap= "A: Distribution of the body diameter of vessels with coefficients of variation by phases. B: Coefficients of variation of vessel shape represented by PC1 in relation to vessel size represented by body diameter, showing more standardization (lower CV values) in vessel form and size in the Chinese period. C: Correlation between shape variables (PC1 and PC2) and body diameter of vessels with Pearson's r and p-values by phases"}
knitr::include_graphics(here("analysis/figures/size-boxplot-regression.jpg"))
```

>>>>

```{r, size-shape-regression-plots, echo=FALSE, fig.cap= "A: Distribution of the body diameter of vessels with coefficients of variation by phases. B: Coefficients of variation of vessel shape represented by PC1 in relation to vessel size represented by body diameter, showing more standardization (lower CV values) in vessel form and size in the Chinese period. C: Correlation between shape variables (PC1 and PC2) and body diameter of vessels with Pearson's r and p-values by phases"}
knitr::include_graphics(here("analysis/figures/plot-size-boxplot-regression.jpg"))
```
